### 2020-05-25 Report/aws_325ghz_study.tex
updated section 6

\subsection{Validation of simulations}
%
Using the simulation setup described above, around 77000 cases were simulated
based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
was made between the observations over water and land.

@@

\subsection{Formulation of correction scheme}
%
Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz
respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
scheme formulates a relationship between the cloud impact in C1 to the TB
differences between C1 and C2:
\begin{equation}
Tb1_{as}-Tb2_{cs} = f(x_m)
\label{eq:TB:diff}
\end{equation}
where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.

The combinations of C1 and C2 are selected by matching their weighting
functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183 and 325\,GHz paired
combinations are possible, for example one such paired combination is AWS-34
and AWS-42. For each of the five 183\,GHz channels, the correction scheme is
derived from its corresponding counterpart in 325\,GHz channel.

@@

It is also important to have a manner for making a clear/cloudy classification.
This is useful for making a filtering in line with \citep{rekha2012potential},
but is also needed in the correction scheme. The later is the case as the
polynomial fit derived gives a non-zero correction for clear-sky cases. In
Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
and C2 (red dots) have a mean close to zero (as the weighting functions are
well matched), but this is not the case for all channel combinations and some
general rule for finding a threshold value (with respect to $x_m$) must be
formulated. The polynomial fit will be used also for this part.

@@

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
dtb_{cs}= f_{cs}^{-1}(x_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitide of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).

@@

\subsection{Application of correction scheme}
\begin{figure}[!p]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=90mm]{PDF_corrected_AWS-34_AWS-42}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The spread of noise is also shown as
      reference. The measurements have been corrected using brightness
      temperatures from AWS-42. }
	\label{fig:correction:c34-42}
\end{figure}
%

@@

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
		\hline
Noise             &   0.00 &  0.63 &              -0.01 &                - \\
uncorrected       &  -0.30 &  1.00 &              -2.64 &                - \\
filtered(1$\sigma$)   &  -0.13 &  0.68 &              -0.25 &             13.05 \\
corrected(1$\sigma$) &  -0.06 &  0.76 &              -0.48 &               13.05 \\
corrected(2$\sigma$) &  -0.11 &  0.75 &              -0.69 &                7.21 \\
Sreerekha et al   &  -0.21 &  0.78 &              -1.02 &               62.15 \\

		\hline
	\end{tabular}
	\caption{Various metrics for different subsets of the measurement dataset. The different datasets are: noise (simulation dataset), uncorrected (measurment dataset), filtered $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with noise-index = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with noise-index = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
	\label{tab:correction:stats:34:42}
\end{table}
%
In this section, we test the applicability of the correction scheme in detail. To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2. Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. As an example, the results from the channel combination AWS-34 and AWS-42 are shown.

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. The clear-sky adjustment for all eligible
measurements (without clear-sky screening) is calculated from all three models,
and the three predicted datasets are compared. The error in the predicted
measurements is assessed by calculating the deviation to noise-free clear-sky
observations. The occurrence frequency of the deviations from three models is
shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the all
measurement without any filtering or correction is also plotted as reference
(orange color). If all measurements are devoid of any cloud impact, the
deviations should follow the gaussian distribution of noise. However, in real
scenarios, the distribution is skewed due to the impact of clouds. It should
also be noted that since no clear-sky screening was included in the
measurements, the measurements with zero deviation to noise-free clear-sky were
reduced. This indicates that it is extremely important to correctly classify
the cases as clear/cloudy. Among the three models, the quadratic and cubic
models work better than the linear model. Both quadratic and cubic models are
able to correct the cloud impact in the measurements, however the values of
average bias indicates that the cubic model performs better. The average
deviation in the dataset is -0.82\,K and after correction with a cubic model,
it reduces to -0.02\,K, while for quadratic model, the average bias after
correction is 0.24\,K. For all other results described in this section, a cubic
model is used.

Before applying the clear-sky screening, the measurement dataset was also
thinned in order to improve the representation of the cloudy cases. Validation
of the simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the
cloudy cases were underrepresented than the observations. Removing 50\% of the
clear-sky cases, helped in improving the percentage of total cloudy cases in
the database. Further in the text, results from only thinned dataset are
described.

To implement the clear-sky screening as discussed in the previous section, two
different values of the noise-index are tested: $1\sigma$ and $2\sigma$, where
$\sigma$ is the standard deviation of noise. For both values of noise-index the
corresponding clear-sky cut-off ($dtb_{cs}$) is calculated using
Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42:thinned} shows the results
when only the screened cloudy cases are corrected/rejected. Various metrics
from the corrected measurements are also shown in
Table~\ref{tab:correction:stats:34:42}. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In their approach, the cases with TB difference between
AWS-4x and AWS-32 greater than 6\,K are classified as cloudy and are rejected.
Assuming that the measurement is cloudy in AWS-32, the corresponding measuremnt
in other 183GHz channels is also rejected. In order to have a fair comparison
of our approach with \cite{rekha2012potential}, we also include a dataset where
all the cloudy cases according to the clear-sky screening are filtered out from
the measurements. The metrics from this dataset are also provided in under
label ``filtered''. For all datasets shown in the table, we assume that cases
with $Tb2-Tb1 < $ -15\,K are ``too-cloudy''.
%Such cases form 5\% of the thinned
%dataset and are not included in the statistics.

The distribution of the deviations in the filtered data (both with approach
described by Sreerekha et al and the clear-sky screening) is non-Gaussian. The
right side of the distribution follows the measurement noise while the left
side is skewed. The skewness in the distribution is due to cloud impacts which
go undetected. These cases have cloud impact less than the threshold value and
are misclassfied as clear. The frequency of such cases is higher in Sreerekha
et al approach than the clear-ksy screening presented here. The measure of
skewness is also smaller for the clear-sky screening. 
%In the report by
%\cite{rekha2012potential} they mention that for 6\,K threshold value, around
%2.4\% of the cloudy cases are misclassfied as clear. For this value of
%threshold, 41\% of the clear cases are also classfied as cloudy and rejected.

The regression approach described here does not provide any way to correct the
misclassfied cases, but the frequency of such cases can be controlled through
clear-sky cutoff ($dtb_{cs}$). When the clear-sky screening is applied to this
dataset, around 13.05\% of the cases are classified as cloudy when $dtb_{cs}$
corresponds to noise-index = 1$\sigma$, while with 2$\sigma$ around 7.2\% are
classified as cloudy. These cloudy cases are corrected according to the cubic
model. After correction, the average deviation to the clear-sky noise-free
values in the corrected measurements should be closer to zero than uncorrected
measurements. Before correction, the average bias for measurements is -0.30\,K
but after correction it reduces to -0.06\,K and -0.11\,K for the two values of
the noise-index respectively. This indicates that a larger value of noise-index
increases the probability of falsely classifying clear cases as cloudy.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

As a reference with respect to having a channel at 229\,GHz, we also apply the
correction scheme described above to correct AWS-32 using AWS-4X (following
\citet{rekha2012potential}). In this case, C1 and C2 are AWS-32 and AWS-4X. The
TB correlations between AWS-32 and AWS-4X are poor and show a large spread
particularly for large cloud impacts (not shown). We fit the data to a
cubic model, but exclude cases with $Tb2-Tb1 <$ -20\,K. Also cases with TB
difference less than 0.2\,K are classified as clear and are not included in the
fit. The clear-sky screening is also evaluated for noise-index = 1$\sigma$ and
$2\sigma$. Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations to
clear-sky values before and after correction, and the corresponding metrics are
provided in Table~\ref{tab:correction:stats:32:4X}. As evident from the figure,
\cite{rekha2012potential} classifies all measurements with cloud impact greater
than 6\,K as cloudy, but a significant skewness in the distribution indicates
misclassfication of cloudy cases. However, the frequency of misclassfied cases
is significantly lower for our clear-sky screening. With
\cite{rekha2012potential}'s approach, around 62\% of the measurements are
rejected as cloudy, but in our approach, 84\% of the cases are classified as
cloudy. This clearly indicates a high rate of misclassification of the clear
cases.
\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
		&   [K]  &   [K] & skewness[K] 		& filtered/corrected [\%]\\
		\hline
Noise             &  -0.00 &  0.45 &               0.02 &                - \\
uncorrected       &  -0.62 &  1.76 &              -4.61 &                - \\
filtered($1\sigma$)  &  -0.21 &  0.52 &              -0.65 &               84.49 \\
corrected($1\sigma$) &   0.88 &  1.76 &              -1.29 &               84.49 \\
corrected($2\sigma$) &   0.76 &  1.80 &              -1.06 &               68.00 \\
Sreerekha et al   &  -0.40 &  1.00 &              -2.54 &               62.02 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
The correction scheme can also be extended to other combinations of 183GHz and
325GHz. The most relevant combinations for clear-sky screening are: AWS-32 and
AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The statistics of the filtered dataset are better than
the approach by \cite{rekha2012potential}, while the corrected data have poorer
statistics. This is not surprising as the weighting function match between 
AWS-32 and  AWS-41 is poor.
%However, a very high rejection
%fraction (85\%) indicates that a large percentage of clear cases are
%misclassfied as cloudy.

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. These TB differences for this combination and the cloud
impact in AWS-33 are highly correlated and using a cubic model, approximately
20\% of the observations are corrected, which reduces the average bias in the
measurements from -0.33\,K to -0.05\,K.

A similar performance is seen for the combination AWS-35 and AWS-43, where 19\%
of the measurements are classfied as cloudy. Correcting these measurements for
the cloud impact reduces the average bias in the measurements from -0.33\,K to
-0.05\,K. Table~\ref{tab:correction:stats:35:43} shows the statistics obtained
from this combination. The statistics from the channel combination AWS-36 and
AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
		\hline
 Noise             &  -0.00 &  0.45 &               0.01 &               - \\
uncorrected       &  -0.48 &  1.82 &             -14.94 &                - \\
filtered(1sigma)  &  -0.20 &  0.55 &              -0.61 &               92.99 \\
corrected(1sigma) &   0.48 &  1.68 &             -15.20 &               92.99 \\
corrected(2sigma) &   0.47 &  1.68 &             -15.16 &               94.75 \\
Sreerekha et al   &  -0.41 &  1.00 &              -2.55 &               62.02 \\	
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction\\
		&   [K]  &   [K] & skewness[K]                   & filtered/corrected [\%]\\
		\hline
	Noise             &  -0.00 &  0.45 &               0.01 &               - \\
	uncorrected       &  -0.33 &  0.91 &              -3.15 &                - \\
	filtered(1$\sigma$)  &  -0.13 &  0.49 &              -0.39 &               20.60 \\
	corrected(1$\sigma$) &  -0.05 &  0.59 &              -0.85 &               20.60 \\
	corrected(2$\sigma$) &  -0.11 &  0.57 &              -1.17 &               10.19 \\
	Sreerekha et al   &  -0.30 &  0.79 &              -2.21 &               62.10 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-33 and AWS-41.   }
	\label{tab:correction:stats:33:41}
\end{table}

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
		&   [K]  &   [K] & skewness[K] & filtered/corrected [\%]\\
		\hline
 Noise             &  -0.00 &  0.63 &              -0.01 &                - \\
uncorrected       &  -0.27 &  1.06 &              -4.44 &                - \\
filtered(1$\sigma$)  &  -0.13 &  0.68 &              -0.47 &               19.02 \\
corrected(1$\sigma$) &   0.01 &  0.90 &              -1.67 &               19.02 \\
corrected(2$\sigma$) &  -0.09 &  0.83 &              -2.39 &                6.37 \\
Sreerekha et al   &  -0.13 &  0.70 &              -0.58 &               62.24 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-35 and AWS-43.   }
	\label{tab:correction:stats:35:43}
\end{table}

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction  \\
		&   [K]  &   [K] & skewness[K] &				filtered/corrected [\%]\\
		\hline
Noise             &  -0.00 &  0.88 &              -0.01 &                - \\
uncorrected       &  -0.16 &  1.01 &              -0.86 &                - \\
filtered(1$\sigma$)  &  -0.11 &  0.92 &              -0.12 &                4.98 \\
corrected(1$\sigma$) &  -0.07 &  0.93 &              -0.07 &                4.98 \\
corrected(2$\sigma$) &  -0.11 &  0.94 &              -0.18 &                2.06 \\
Sreerekha et al   &  -0.09 &  0.91 &              -0.10 &               62.20 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-36 and AWS-43.   }
	\label{tab:correction:stats:36:43}
\end{table}

>>>>

\subsection{Validation of simulations}
\label{sec:validation}
%
Using the simulation setup described above, around 77000 cases were simulated
based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
was made between the observations over water and land.

@@

\subsection{Formulation of correction scheme}
\label{sec:correction:scheme}
%
Let C1 and C2 represent the one of the channels each from 183\,GHz and 325\,GHz
respectively, and Tb1 and Tb2 represent the corresponding TB. The correction
scheme formulates a relationship between the cloud impact in C1 to the TB
differences between C1 and C2:
\begin{equation}
Tb1_{as}-Tb2_{cs} = f(x_m)
\label{eq:TB:diff}
\end{equation}
where, $x_m = Tb2_{as} - Tb1_{as}$, and the subscripts ``as'' and ``cs'' denote the all-sky and clear-sky cases respectively.

The combinations of C1 and C2 are selected by matching their weighting
functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183\,GHz and 325\,GHz paired
combinations are possible, for example one such paired combination is AWS-34
and AWS-42. For each of the five 183\,GHz channels, the correction scheme is
derived from its corresponding counterpart in 325\,GHz channel.

@@

It is also important to have a manner for making a clear/cloudy classification.
This is useful for making a filtering in line with \citep{rekha2012potential},
but is also needed in the correction scheme. The latter is the case as the
polynomial fit derived gives a non-zero correction for clear-sky cases. In
Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
and C2 (red dots) have a mean close to zero (as the weighting functions are
well matched), but this is not the case for all channel combinations and some
general rule for finding a threshold value (with respect to $x_m$) must be
formulated. The polynomial fit will be used also for this part.

@@

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T).

@@

\subsection{Application of correction scheme}
\begin{figure}[!p]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=90mm]{PDF_corrected_AWS-34_AWS-42}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The spread of noise is also shown as
      reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The average bias values are given in parenthesis in the legend. No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > 15$\,K are rejected.}
	\label{fig:correction:c34-42}
\end{figure}
%

@@

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
		noise             		&   0.00 &  0.63 &              -0.00 &                - \\
		uncorrected       		&  -0.19 &  0.87 &              -2.42 &                - \\
		filtered($1\sigma$ ) 	&  -0.10 &  0.66 &              -0.15 &               10.56 \\
		corrected($1\sigma$) 	&  -0.05 &  0.72 &              -0.23 &                2.84 \\
		corrected($2\sigma$) 	&  -0.09 &  0.70 &              -0.49 &                2.84 \\
		sreerekha et al   		&  -0.14 &  0.73 &              -0.76 &               61.73 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation(std), and measure of skewness of deviations of the measurements to noise-free clear-sky cases. The fraction rejected describes the percentage of cases which are removed. The different datasets are: noise (simulation dataset), uncorrected (measurement dataset), filtered $1\sigma$ (cloudy measurements are filtered with $dtb_{cs}$ = 1$\sigma$), corrected $1\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 1$\sigma$), corrected $2\sigma$ (cloudy measurements are corrected with $dtb_{cs}$ = 2$\sigma$), Sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential}).   }
	\label{tab:correction:stats:34:42}
\end{table}
%
\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction  \\
		&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
noise             		&   0.00 &  0.63 &              -0.01 &                - \\
uncorrected       		&  -0.29 &  1.00 &              -2.62 &                - \\
filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.24 &               17.49 \\
corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.97 \\
corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.97 \\
sreerekha et al   		&  -0.20 &  0.79 &              -1.01 &               63.09 \\
		\hline
\end{tabular}
\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for thinned dataset. 50\% of the clear cases are removed to improve the improve the representation of cloudy cases }
\label{tab:correction:stats:34:42:thinned}
\end{table}
%
In this section, we test the applicability of the correction scheme in detail. To analyse the performance of the approach, we apply it to correct the measurements from C1 using data from C2. Without the availability of actual data, the simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. As an example, the results from the channel combination AWS-34 and AWS-42 are shown.

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. The clear-sky adjustment for all eligible
measurements (without clear/cloudy classification) is calculated from all three models,
and the three predicted datasets are compared. The error in the predicted
measurements is assessed by calculating the deviation to noise-free clear-sky
observations. The occurrence frequency of the deviations from three models is
shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the
measurement without any filtering or correction is also plotted as reference
(orange color). If all measurements are devoid of any cloud impact, the
deviations should follow the gaussian distribution of noise. However, in real
scenarios, the distribution is skewed due to the impact of clouds. It should
also be noted that since no clear-sky screening was included in the
measurements, the measurements with zero deviation to noise-free clear-sky were
reduced. This indicates that it is extremely important to correctly classify
the cases as clear/cloudy. Among the three models, the quadratic and cubic
models work better than the linear model. Both quadratic and cubic models are
able to correct the cloud impact in the measurements, however the values of
average bias indicates that the cubic model performs better. The average
deviation in the dataset is -0.82\,K and after correction with a cubic model,
it reduces to -0.02\,K, while for quadratic model, the average bias after
correction is 0.24\,K. For all other results described in this section, a cubic
model is used.

To implement the clear/cloudy classification as discussed in the previous section, two
different values of $dtb_{cs}$ are tested: $1\sigma$ and $2\sigma$. For both values of $dtb_{cs}$ the
corresponding clear-sky cut-off ($x_{cs}$) is calculated using
Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and corrected measurements to their noise-free clear-sky values. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to have a fair comparison
of our approach with \cite{rekha2012potential}, we also include the dataset,``Filtered'', where all cloudy cases are rejected.  Apart from the fit based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy'', and are rejected.
Various metrics corresponding to the Figure~\ref{fig:correction:c34-42} are shown in
Table~\ref{tab:correction:stats:34:42}.

The distribution of the deviations in the pure-filtered data is non-Gaussian. The
right side of the distribution follows the measurement noise while the left
side is skewed. The skewness in the distribution is due to cloud impacts which
go undetected. The frequency of such cases is higher in Sreerekha in comparison to the correction scheme presented here. The regression approach described here does not provide any way to correct the misclassfied cases, but the frequency of such cases can be controlled through $dtb_{cs}$. With a fit based cloudy classification, around 7\% of the cases are classified as cloudy when $dtb_{cs}$
= 1$\sigma$.  After correction, the average deviation to the clear-sky noise-free
values in the corrected measurements should be closer to zero than uncorrected
measurements. Before correction, the average bias for measurements is -0.19\,K
but after correction it reduces to -0.05\,K and -0.09\,K for the two values of
the $dtb_{cs}$ respectively.

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were underrepresented in comparison to the observations. In order to have a better representation of the cloudy cases, we thin the measurement dataset by rejecting 50\% of the clear-sky cases. Results from this smaller dataset are shown in Table~\ref{fig:correction:c34-42:thinned}. In comparison to the original dataset, the statistics in the thinned dataset is slightly worse, as expected. But overall the performance of the correction scheme is comparable. For all further analysis presented in this report, we use the thinned dataset.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

As a reference with respect to having a channel at 229\,GHz, we also apply the
correction scheme described above to correct AWS-32 using AWS-4X (following
\citet{rekha2012potential}). In this case, C1 and C2 are AWS-32 and AWS-4X. The
TB correlations between AWS-32 and AWS-4X are poor and show a large spread
particularly for large cloud impacts (not shown). We fit the data to a polynomial model as described in Sec.~\ref{sec:correction:scheme} but exclude cases with $Tb2-Tb1 <$ -20\,K in the fit.

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the measurements to
clear-sky values before and after correction, and the corresponding metrics are
provided in Table~\ref{tab:correction:stats:32:4X}. Rejecting all the cloudy cases reduces the average bias in the measurements from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias increases to 0.87\,K. This indicates that the relationship between AWS-32 and AWS-4X is inadequate to estimate the cloud impact in AWS-32.
% 
\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
						&   [K]  &   [K] & skewness[K] 		& rejected [\%]\\
		\hline
Noise             		&  -0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
filtered($1\sigma$)  	&  -0.22 &  0.51 &              -0.65 &               85.37 \\
corrected($1\sigma$) 	&   0.87 &  1.75 &              -1.31 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.08 &                5.35 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.95 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

\subsection{Application of correction scheme to AWS-32, AWS-33, AWS-35 and AWS-36}
%
The correction scheme can also be extended to other combinations of 183GHz and
325GHz. The most relevant combinations for clear-sky screening are: AWS-32 and
AWS-41; AWS-33 and AWS-41; AWS-35 and AWS-43; AWS-36 and AWS-43.

Table~\ref{tab:correction:stats:32:41} shows the statistics when AWS-32 is
corrected using AWS-41. The statistics of the filtered dataset are better than
the approach by \cite{rekha2012potential}, while the corrected data have poorer
statistics. This is not surprising as the weighting function match between 
AWS-32 and  AWS-41 is poor.

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the average bias in the measurements from -0.33\,K to -0.13\,K, while a correction of cloudy cases according to the correction scheme reduces the bias further to 0.01\,K.

A similar performance is seen for the combination AWS-35 and AWS-43, where 21\%
of the measurements are classfied as cloudy. Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this combination. The statistics from the channel combination AWS-36 and AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
%
\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
noise             		&   0.00 &  0.45 &               0.00 &                - \\
uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.30 &               72.27 \\
corrected($1\sigma$) 	&   0.44 &  1.70 &             -14.68 &                7.93 \\
corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.85 &                7.93 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.04 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure  & fraction\\
						&   [K]  &   [K] & skewness[K]  & rejected [\%]\\
		\hline
	noise       	    	&  -0.00 &  0.45 &               0.00 &               - \\
	uncorrected	    		&  -0.33 &  0.91 &              -3.15 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.49 &              -0.40 &               26.13 \\
	corrected($1\sigma$) 	&  -0.05 &  0.59 &              -0.85 &                6.87 \\
	corrected($2\sigma$) 	&  -0.11 &  0.57 &              -1.17 &                6.87 \\
	sreerekha et al   		&  -0.30 &  0.79 &              -2.21 &               62.99 \\

		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-33 and AWS-41.   }
	\label{tab:correction:stats:33:41}
\end{table}

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
 Noise           	  &  -0.00 &  0.63 &               0.00 &                -\\
uncorrected     	  &  -0.27 &  1.06 &              -4.42 &                - \\
filtered($1\sigma$)	  &  -0.13 &  0.68 &              -0.46 &               21.42 \\
corrected($1\sigma$)  &   0.01 &  0.90 &              -1.66 &                2.87 \\
corrected($2\sigma$)  &  -0.09 &  0.83 &              -2.37 &                2.87 \\
sreerekha et al  	  &  -0.13 &  0.70 &              -0.58 &               63.10 \\

		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-35 and AWS-43.   }
	\label{tab:correction:stats:35:43}
\end{table}

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction  \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
 Noise            	 &  -0.00 &  0.88 &              -0.01 &               - \\
uncorrected      	 &  -0.16 &  1.02 &              -0.86 &                - \\
filtered($1\sigma$)  &  -0.11 &  0.92 &              -0.13 &                7.39 \\
corrected($1\sigma$) &  -0.07 &  0.93 &              -0.07 &                2.50 \\
corrected($2\sigma$) &  -0.11 &  0.94 &              -0.19 &                2.50 \\
sreerekha et al 	 &  -0.09 &  0.91 &              -0.11 &               63.11 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-36 and AWS-43.   }
	\label{tab:correction:stats:36:43}
\end{table}
